Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-02-24 Manuscript_TIFS/manuscript_TIFS.tex
Conlusion grammer update

\section{Conclusion}
In this paper, we have designed an FL architecture, Ensemble Federated Learning (called EFL) in this study, which allows knowledge transferring between the FL server and FL clients via the unlabeled dataset and FL clients' predictions of it. We have crafted the FLPhish technique to make EFL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust. We have proved the security of FLPhish scheme against backdoor attacks. At last, we have tested our suggested FLPhish in a variety of scenarios. The results of the experiment demonstrate the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL. 
\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.

>>>>

\section{Conclusion}
In this paper, we have designed an FL architecture, Ensemble Federated Learning (called EFL), which allows knowledge transfer between the FL server and FL clients via an unlabeled dataset and the FL clients' predictions of it. We have crafted the FLPhish technique to make EFL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we have proposed a reputation technique based on Bayesian inference to determine a client's level of trust. We have proved the security of the FLPhish scheme against backdoor attacks. Finally, we have tested our suggested FLPhish in a variety of scenarios. The results of the experiment demonstrate the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL. 
\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving the FLPhish scheme's efficiency.
